\newpage
\section{Requested modules/funds}


\subsection{Basic Module}

	\subsubsection{Funding for Staff}

		The described work packages WP\ref{wp:generation} and WP\ref{wp:maintenance} represent concisely formulated and sufficiently rich topics for one PhD student each (or Postdoc). 
		The topics are distinctively separated, but do require collaboration, particularly in WP\ref{wp:implementation} where research results are integrated into a prototype system
		that is jointly produced. The realization of the project's goals depends equally on both research aspects.\\

		{\bf 2 PhD student or PostDocs (i.e., 2 TV-L E13) for 24 months}
		

	\subsubsection{Direct Project Costs}

		\paragraph{Equipment up to Euro 10,000, Software and Consumables}$\,$\medskip\\

			We plan to run scalability experiments using Amazon's Web Services, primarily the EC2 computing cloud.
			Estimated cost of running experiments on 16 ``large'' (7.5 GB memory, 2 virtual cores, 850 GB storage) 
			instances at a utilization of 40 hours per months:\\

			{\bf	2000 \euro\xspace per year}\\

			\noindent The remaining expenses, if any, will be paid by the group's regular budget.			

		\paragraph{Travel Expenses}$\,$\medskip\\

		We plan contributions to first-rate international conferences such as The Very Large Database Conference (VLDB), ACM SIGMOD, 
		the ACM Conference on Information and Knowledge Management (CIKM), ACM-SIAM Symposium on Discrete Algorithms (SODA) and, ACM Symposium on the Theory of Computing (STOC). For three such conference visits at international places, we estimate a total cost of \\

		{\bf	6000 \euro\xspace per year.} \\

		\noindent The remaining expenses, if any, will be paid by the group's regular budget.

		\paragraph{Visiting Researchers (excluding Mercator Fellows)}

		\paragraph{Expenses for Laboratory Animals}

		\paragraph{Other Costs}

		\paragraph{Project-related publication expenses}

	\subsubsection{Instrumentation}
		\paragraph{Equipment exceeding Euro 10,000}$\,$\medskip\\
Does not apply.
		\paragraph{Major Instrumentation exceeding Euro 50,000}$\,$\medskip\\
Does not apply.
\subsection{Module Temporary Position for Funding}
Does not apply.
\subsection{Module Replacement Funding}
Does not apply.
\subsection{Module Temporary Clinician Substitute}
Does not apply.
\subsection{Module Mercator Fellows}
Does not apply.
\subsection{Module Workshop Funding}
Does not apply.
\subsection{Module Public Relations Funding}
Does not apply.
%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Project requirements}

\subsection{Employment status information}
%	 For each applicant, state the last name, first name, and employment status (including duration of contract and funding body, if on a fixed-term contract).

	\begin{itemize}
	\item Dr.-Ing. Avishek Anand
		\begin{itemize}
		\item fixed-term contract
		\end{itemize}
	\end{itemize}

\subsection{First-time proposal data}
\begin{itemize}
	\item  Dr.-Ing. Megha Khosla% is a first-time applicant.
	\item  Dr.-Ing. Avishek Anand% is a first-time applicant.
	
\end{itemize}

\subsection{Composition of the project group}
\small
\begin{tabular}{|p{0.20\columnwidth}|p{0.219\columnwidth}|p{0.19\columnwidth}|p{0.18\columnwidth}|p{0.15\columnwidth}|} \hline 
{\bf Name} & {\bf Area/Field of \newline Research} & {\bf Institution} & {\bf Hours per Week \newline (advisory=A)} & {\bf Type of \newline Funding}\\ \hline \hline
Dr.-Ing. Avishek Anand & L3S Research Center & Leibniz University, Hannover  & A & TVL-14 \\ \hline
Dr.-Ing. Megha Khosla & L3S Research Center & Leibniz University, Hannover & 8h & - \\ \hline
\end{tabular}

\subsection{Cooperation with other researchers}

	\subsubsection{Researchers with whom you have collaborated scientifically within the past three years}

	\begin{itemize}
		\item Prof. Dr.-Ing. Gerhard Weikum, Max-Planck-Institut Informatik, Saarbr{\"u}cken, Germany.
		\item Prof. Dr.-Ing. Wolfgang Nejdl, L3S Research Center, Hannover, Germany.
		\item Prof. Dr.-Ing. Sebastian Michel, University of Kaiserslautern, Kaiserslautern, Germany
	\end{itemize}

\subsection{Scientific equipment}
		List larger instruments that will be available to you for the project. 
		These may include large computer facilities if computing capacity will be needed. 

\begin{itemize}
\item 8 DELL servers with 3TB RAID-5 local storage, 50GB main memory, 2x quad-core CPU, each.
\item 1 DELL server with 3TB RAID-5 local storage, 256GB main memory,  2x quad-core CPU.
\end{itemize}


\subsection{Project-relevant interests in commercial enterprises}

None.
%%%%%%%%%%%%%

\section{Additional information}

