\workpackage{Practical Semi-streaming model and Algorithms}
\label{wp:algos}

In~\cite{ballsbins} we proposed an algorithm, which we call \emph{local search allocation}, finds maximum cardinality matching in linear time with high probability. Our approach in~\cite{ballsbins} operates by assigning labels to vertices in $V$. The vertices for augmenting path are chosen based on their labels. The labels are so updated such that at any time the label of a vertex is atmost the shortest distance to an unmatched vertex. In addition to the efficiency of the approach, the algorithm never runs in loops and gives the information when the vertex cannot be matched. The time complexity of the algorithm is $O(|E|)$ and the space complexity is $O(|V|)$. This approach is different from the greedy approach which is commonly employed in such a model in the sense that it allows the matching to change as and when necessary. This means that once an edge is selected for the matching, it can be kicked out later on as and when required.

Even though this algorithm has been designed for a more specific class of bipartite graphs, it can be applied directly on more general bipartite graphs. We focus on the following research questions.

With (i) $O(n poly \log n)$ space and  (ii) amortized $O(1)$ time processing of each edge
\begin{itemize}
\item  \textsf{[RQ I]} Can we achieve an approximation ration closer to the known lower bound $(e/(e-1))$ for general bipartite graphs ?
\item \textsf{[RQ II]} What approximation ratios can we achieve with high probability on different models of random graphs like uniformly random or power law graphs ?
\item \textsf{[RQ III]} What approximation ratios can we achieve for weighted $b$ matchings in bipartite graphs?

\end{itemize}


